A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-11 4_method.tex
make transition length into function depending on bead lower count

\begin{enumerate}
\item Compute a skeletonization of the outline shape based on the Voronoi diagram.
\item Use a significance measure to mark portions of the skeleton which lie in the center.
\item Determine the bead count values in the marked regions and handle transitions in bead count values.
\item Generate ticks along non-marked bones of the skeleton and connect the ticks together to extract the toolpaths.
\end{enumerate}

@@

We define a beading strategy as the following set:
$$
\left\{ b(d), p(n), W(n, d), L(n, d), t, \alpha_{\text{max}} \right\}
$$
where
$b(d)$ gives the optimal bead count to cover a total distance of $d$,
$p(n)$ gives the optimal total distance of a given bead count $n$,
$W(n, d)$ gives the sequence of bead widths to cover a distance $d$ using $n$ beads,
$L(n, d)$ gives the sequence of toolpath positions as distances from the outline to cover a distance $d$ using $n$ beads,
$t$ is the length of transitions within which we switch to a different number of beads
and
$\alpha_{\text{max}}$ is the limit bisector angle of the significance measure.

We call a distance $d$ `prefered' when $d = p(b(d))$
For our method we require the inverse $b^{-1}(n)$ which gives the smallest $d$ for which $b(d) = n$.

The following restrictions hold:
\begin{itemize}
\item $b(d) \geq 0, W(n,d) > 0, L(n, d) \geq 0, t \geq 0$
\item $120\degree < \alpha_{\text{max}} \leq 180\degree$
\item $W$ is symetric: $W(n, d)_i = W(n, d)_{n-i-1}$
\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
\item $p$ is within the range of optimal: $b^{-1}(n) < p(n) < b^{-1}(n + 1)$
%\item $b \left( p(n) \right) = n$ % follows from the above!
\item $b$ is monotonic: $ b(d) \leq b(d + \epsilon)$
\item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
\item $t$ is viable: $\forall i \in \mathbb{N} : t < \left( p(i + 1) - p(i) \right) /{2 \cos \alpha_\text{max}}$
\end{itemize}

>>>>

\begin{enumerate}
\item Compute a skeletonization of the outline shape based on the Voronoi diagram.
\item Use a significance measure to mark portions of the skeleton which lie in the center.
\item Determine the bead count values in the marked regions and handle transitions to different bead count values.
\item Generate ticks along non-marked bones of the skeleton and connect the ticks together to extract the toolpaths.
\end{enumerate}

@@

We define a beading strategy as the following set:
$$
\left\{ b(d), p(n), W(n, d), L(n, d), t(n), \alpha_{\text{max}} \right\}
$$
where
$b(d)$ gives the optimal bead count to cover a total distance of $d$,
$p(n)$ gives the optimal total distance of a given bead count $n$,
$W(n, d)$ gives the sequence of bead widths to cover a distance $d$ using $n$ beads,
$L(n, d)$ gives the sequence of toolpath positions as distances from the outline to cover a distance $d$ using $n$ beads,
$t(n)$ is the length of the transition region to switch from $n$ to $n+1$ beads
and
$\alpha_{\text{max}}$ is the limit bisector angle of the significance measure.

We call a distance $d$ `preferred' when $d = p(b(d))$
For our method we require the inverse $b^{-1}(n)$ which gives the smallest $d$ for which $b(d) = n$.

The following restrictions hold:
\begin{itemize}
\item $b(d) \geq 0, W(n,d) > 0, L(n, d) \geq 0, t \geq 0$
\item $120\degree < \alpha_{\text{max}} \leq 180\degree$
\item $W$ is symetric: $W(n, d)_i = W(n, d)_{n-i-1}$
\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
\item $p$ is within the range of optimal: $b^{-1}(n) < p(n) < b^{-1}(n + 1)$
%\item $b \left( p(n) \right) = n$ % follows from the above!
\item $b$ is monotonic: $ b(d) \leq b(d + \epsilon)$
\item $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} < \infty$.
\item $t$ is viable: $t(n) < \left( p(n + 1) - p(n) \right) /{2 \cos \alpha_\text{max}}$
\end{itemize}
